
\cvsection{Education}

\cveventSameLine{\linked[0]{Georgia Institute of Technology}{https://www.gatech.edu}}
    {\linked[0]{M.S. in Computer Science}{https://www.cc.gatech.edu/degree-programs/master-science-computer-science}}
    {Aug. 2023 - Dec. 2025}{Atlanta, GA}
\begin{itemize}
    \item GPA: 4.0/4.0 - \linked{Transcript}{https://drive.google.com/file/d/1d8YsHVGGYXTqwO-0FZjeuxpByIEFsraX/view?usp=sharing}
    % \item Featured courses: Machine Learning; Natural Language; Deep Learning for Text Data; Large Language Models; Game Artificial Intelligence; Data-Centric Machine Learning
    \item Featured courses: Machine Learning; Natural Language Processing; Deep Learning for Text Data; Large Language Models; Game AI; Data-Centric ML
\end{itemize}
% \divider
\dividerSmall



\cveventSameLine{\linked[0]{University of Michigan}{https://umich.edu}}
    {\linked[0]{B.S. in Computer Science}{https://cse.engin.umich.edu}}
    {Sep. 2020 - Apr. 2022}{Ann Arbor, MI}
\begin{itemize}
    \item GPA: 3.98/4.0 - \linked{Transcript}{https://drive.google.com/file/d/1cXDQv8PgRQ2GGUN9pupWWdQcZ0xIVtvi/view?usp=sharing}
    % \item Featured courses: Data Structures \& Algorithms; Computer Organization;
    %     Foundation of Computer Science; Machine Learning; Artificial Intelligence;
    %     Conversational AI; Natural Language Processing; Deep Learning for Computer Vision;
    %     Linear Algebra; Statistics \& Data Analysis\hspace{-0.25em}
    \item Featured courses: Data Structures \& Algorithms; Computer Organization;
    CS Theory; ML; Artificial Intelligence;
    Conversational AI; NLP
    % DL for CV
    % Linear Algebra; Statistics \& Data Analysis\hspace{-0.25em}
\end{itemize}
% \divider
\dividerSmall



\cveventSameLine{\linked[0]{University of Maryland}{https://www.umd.edu}}
    {\linked[0]{B.S. in Computer Science}{https://www.cs.umd.edu}}
    {Aug. 2018 - May. 2020}{College Park, MD}
\begin{itemize}
    \item GPA: 3.97/4.0 - \linked{Transcript}{https://drive.google.com/file/d/1L75BLD-GpzKqhYnGOUk0VjGjNUoivliI/view?usp=sharing}
    \item Featured Courses: Data Structures \& Algorithms; Computer Systems;
        Discrete Mathematics; Programming Languages

    \iftoggle{compact}{
        \item Featured Courses: 2D \& 3D Design; Drawing; Digital Art \& Design
    }{
        \item Featured Courses:
            % Applied Probability \& Statistics; Logic;
            Applied Statistics; Logic;
            2D \& 3D Design; Drawing; Digital Art \& Design;
            Morals \& Ethics
    }
\end{itemize}
\dividerSmall



\iftoggle{compact}{%
    %
}{%
    \cveventSameLine{\linked[0]{High School Affiliated to Renmin Univ. of China}{https://www.linkedin.com/company/high-school-affiliated-to-renmin-university-of-china-rdfz-icc/}}%
        {High School Diploma}%
        {Aug. 2015 - Jul. 2018}{Beijing, CN}%
    \begin{itemize}%
        \item GPA: 3.93/4.0%
        \item Featured A-Level Courses: Further Mathematics, Computer Science, Economics, Physics%
    \end{itemize}%
    \dividerSmall
}%